---
title: "3D Plotting"
author: "Andre Cavalcanti"
date: "June 23, 2016"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mosaic)
library(plotly)
library(shiny)
```

### Summary/Instructions

This shiny app reads data from a file into a dataframe, gets the names of the variables in the dataframe and allows you to pick which to use to create a 3D using plotly.

Plotly is an awesome javascript library to make interactive graphs.


#### Reading the file

Change dataBirds.csv to the name of your file:
```{r}
myData <- read.csv("dataBirds.csv")
myList <- colnames(myData)  # [2:length(myData)]
myList[1] <- " "
```

#### Summary of your data

Here is your data frame:
```{r}
tableOutput(outputId = "dataToShow")
```

```{r}
output$dataToShow <- 
  renderTable(head(myData), options = list(pageLength = 5))
```

#### Plotting:

Choose the variables to plot:

```{r}

sidebarLayout(

    sidebarPanel(
      selectInput(inputId = "axisX", label = "X axis:", choices = myList, selected = myList[1]),
      selectInput(inputId = "axisY", label = "Y axis:", choices = myList, selected = myList[1]),
      selectInput(inputId = "axisZ", label = "Z axis:", choices = myList, selected = myList[1]),
      selectInput(inputId = "myColor", label = "Marker Color By:", choices = myList, selected = myList[1]),
      selectInput(inputId = "mySize", label = "Marker Size By:", choices = myList, selected = myList[1]),
      selectInput(inputId = "myShape", label = "Glyph Shape By: (pick a factor variable)", choices = myList, selected = myList[1])
    ),

    mainPanel(
      plotlyOutput(outputId = "d_plot")
    )
  )

```


```{r}
output$d_plot <-
  renderPlotly(
    {
      plot_ly(myData, 
              x = myData[[input$axisX]], 
              y = myData[[input$axisY]], 
              z = myData[[input$axisZ]], 
              type = "scatter3d", 
              mode = "markers", 
              text = paste("File: ", Name), 
              color = myData[[input$myColor]], 
              size = myData[[input$mySize]], 
              symbol = myData[[input$myShape]]
              ) %>%
        layout(title = " Your graph",
               scene = list(
                  xaxis = list(title = input$axisX),
                  yaxis = list(title = input$axisY),
                  zaxis = list(title = input$axisZ)
                  )
              )
    }
  )

```

